---
title: "Text mining - Semantic Analysis"
author: "Toke Jøns Mulvad"
date: "29/12/2020"
output: html_document
---
# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install and run the necessary packages
```{r, load librarys}
library(tidyverse)
library(pdftools)
library(tidytext)
library(textdata)
library(here)
```

## Pre-processing the Text
Download the annual reports from https://soeg.kb.dk/permalink/45KBDK_KGL/1pioq0f/alma99122083396305763 and create "texts" folder into which the reports are placed.
I have named the files after the following pattern: "AarVrids_YYYY_YYYY.pdf" 
To analyse the entire textcorpus, the files are combined, using the "pdf_combine" function, the combined pdf is named textcorpus.pdf
```{r}
pdf_combine(c("texts/AarVrids_1861_1865.pdf", "texts/AarVrids_1866_1870.pdf", "texts/AarVrids_1871_1875.pdf", "texts/AarVrids_1876_1880.pdf", "texts/AarVrids_1881_1891.pdf", "texts/AarVrids_1892_1899.pdf", "texts/AarVrids_1900_1910.pdf", "texts/AarVrids_1911_1913.pdf", "texts/AarVrids_1913_1924.pdf", "texts/AarVrids_1924_1950.pdf"), "textcorpus.pdf")
```

The corpus of more that 5700 pages is then loaded into R 
```{r}
docs_path <- here("texts","textcorpus.pdf")
docs_corpus <- pdf_text(docs_path)
```

After loading the corpus into R each page then become searchable
```{r}
text_p106 <- docs_corpus[106]
text_p106
```

### Wrangling Data
Lines are separated by lines ("\n"), done with the "stringr::str_split()" function. They are then unnested into regular columns using "tidyr::unnest()". Lastly unnecessary spaces are removed by "stringr::str_trim()"
```{r}
docs_df <- data.frame(docs_corpus) %>% 
  mutate(text_full = str_split(docs_corpus, pattern = '\\n')) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full)) 
```

#### Tokens in Tidy Format
Each word is put in its own column using "tidytext::unnest_tokens"
```{r}
docs_tokens <- docs_df %>% 
  unnest_tokens(word, text_full)
#Which give a table of 1.066.629 columns
```

The words can then be counted
```{r}
docs_wc <- docs_tokens %>% 
  count(word) %>% 
  arrange(-n)
#Adds up to 61.035 words
```

Removing stopwords makes later analysis more meaningful
```{r}
docs_stop <- docs_tokens %>% 
  anti_join(stop_words) %>% 
  select(-docs_corpus)
```

Afterwards a new count of words can be made, now without any of the stopwords
```{r}
docs_swc <- docs_stop %>% 
  count(word) %>% 
  arrange(-n)
#Without stopwords there are 906.932 columns 
```

It can also be useful to remove any numbers from the corpus while words are kept 
```{r}
docs_no_numeric <- docs_stop %>% 
  filter(is.na(as.numeric(word)))
#After removing numbers there are 773.579 columns left
```

```{r}
length(unique(docs_no_numeric$word))
#And so, there are 56695 unique words in the corpus
```

#### Semantic analysis with afinn: 
Download the afinn semantic lexicon
```{r}
get_sentiments("afinn")
```

Bind words in `docs_stop` to `afinn` lexicon
```{r}
docs_afinn <- docs_stop %>% 
  inner_join(get_sentiments("afinn"))
```

The semantics can then be set into a graph based on the -5 to +5 afinn ranking
```{r}
docs_afinn_hist <- docs_afinn %>% 
  count(value)
ggplot(data = docs_afinn_hist, aes(x = value, y = n)) +
  geom_col()
```

Lastly we can then look at the total of the scoring: 
```{r}
docs_summary <- docs_afinn %>% 
  summarize(
    mean_score = mean(value),
    median_score = median(value)
  )
#The mean for the corpus is just on the positive site of the ranking system (0.35) and the median score is also near the middle but nonetheless positive (+1)
```